%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../WeizhouPan_en.tex"
%%% End:

\section{\hei Education}

\tlcventry{2015.9}{0}{College of Chemistry and Molecular Engineering, Peking University}{}{}{}{Graduate student (2020 graduation), Theoretical and Computational Chemistry. Advisor: Prof. Hong Jiang}

\tlcventry{2011.9}{2015.7}{College of Chemistry and Molecular Engineering, Peking University}{}{}{}{B. Sc. in Chemistry. GPA: 3.41/4}

\section{Skills}

\cvcomputer{Theory Tools}{Density functional theory, many-body theory}
           {Softwares}{VASP, \textsc{WIEN2k}, \textsc{Abinit}, \textsc{GPAW}, \textsc{FHI-gap}}
\cvcomputer{Programming}{Python, Fortran, Shell/Bash, MPI, C (basics)}
           {Libraries}{Intel{\textregistered} MKL, spglib, FFTW3, \textsc{Phonopy}, \textsc{ASE}}
           
\cvcomputer{Dev. Tools}{Vim, VS Code, Git, Makefile, Mathematica{\textregistered}}
           {Visualization}{Matplotlib, XmGrace, Adobe{\textregistered} Photoshop}
\cvcomputer{Document}{\LaTeX{}, Markdown, Jupyter Notebook}
           {Foreign Lang.}{CET6 (550), JLPT N1 (113)}{}{}

\section{Experience}

\subsection{Scientific Projects}

\tlcventry{2017.9}{0}{Development and Implementation of First-principles Electronic Structure Method Beyond Density Functional Theory Within LAPW Framework}{Ph.D. project}{}{}
{
    \begin{itemize}%
        \item
        Test, maintain and optimize the home-brew Fortran program \textsc{FHI-gap} for all-electron $GW$ calculations based on many-body perturbation theory.
        \item Derived the representation of truncated Coulomb interaction within mixed product basis, and demonstrated its efficient acceleration for the convergence of self-energy of low-dimensional electronic systems with respect to the vacuum size.
        \item Implemented all-electron ACFDT-RPA functionality, and tested its interface to \textsc{WIEN2k} and reliability of parallelization.
    \end{itemize}
}

\tlcventry{2016.8}{2017.3}{Theoretical Study on the Catalytic Performance of Core-Shell Fe@FeP Nanoparticles for Hydrogen Generation Reaction (HER)}{collaborative project}{}{}
{
    \begin{itemize}
        \item Built atomistic models for Fe@FeP and their H-adsorption counterparts with different interfaces, surfaces and adsorption sites, and perform first-principles calculations for total energy.
        \item Demonstrated the exceptional catalytic performance observed experimentally by predicting a close-to-zero change in Gibbs free energy for the anode reaction at Fe@FeP, with calculations taking zero-point energy and vibration entropy into account.
    \end{itemize}
}

\tlcventry{2015.12}{2018.4}{Theoretical Study on Thermodynamic Stability of Iron Disulfide \ce{FeS2} Polymorphs}{Ph.D. project}{}{}
{
    \begin{itemize}%
        \item Correctly reproduced the experimentally observed enthalpy of transformation from \ce{FeS2} pyrite phase to marcasite by accurate ACFDT-RPA calculation and vibrational zero-point energy from phonon calculation.
        \item Interpreted the thermodynamic stability of pyrite by  designing an effective bandgap as a descriptor of band structure to capture the trend of RPA correlation energy when varying crystal volume.
    \end{itemize}
}

\tlcventry{2017.10}{0}{Python Scripts Set \texttt{mykit} for Pre- and Post-Processing IOs of First-principles Code Packages}{independent code}{}{}
{
    \begin{itemize}%
        \item Support several famous packages and use keyword mapping to allow conversion between input files for different packages.
        \item Open-sourced on GitHub. Continuous integration, automatic test and coverage (77.2\% with 4061 SLOC).
    \end{itemize}
}

\subsection{Student Affairs}
{
\tlcventry{2015.9}{2017.7}{Branch Secretary}{ CCP branch of graduate students from Class 2015, CCME, PKU}{}{}
{
%    \begin{itemize}%
%        \item .
%    \end{itemize}
}
}

\section{\hei Publications}
{
\setlength{\parskip}{-6pt}
\tldatelabelcventry{2019/9}{2019.9}{1\textsuperscript{st} author}{Preprint}{Electronic Band Structure of Cuprous and Silver Halides: an All-Electron $GW$ Study. \href{https://arxiv.org/abs/1906.02472}{arXiv:1906.02472 (2019)}}{}{}
\setlength{\parskip}{-8pt}
\tldatelabelcventry{2018/10}{2018.10}{3\textsuperscript{rd} author}{IF=7.329}{Doubly Screened Hybrid Functional: an Accurate First-Principles Approach for Both Narrow- and Wide-Gap Semiconductors. \textit{J. Phys. Chem. Lett.}  $\mathbf{2018}$, \textit{9}, \href{dx.doi.org/10.1021/acs.jpclett.8b00919}{2338-2345}}{}{}
\setlength{\parskip}{-8pt}
\tldatelabelcventry{2018/3}{2018.3}{1\textsuperscript{st} author}{IF=10.733}{Relative Stability of \ce{FeS2} Polymorphs with the Random Phase Approximation Approach. \textit{J. Mater. Chem. A} $\mathbf{2018}$, \textit{6}, \href{https://pubs.rsc.org/en/content/articlelanding/2018/ta/c8ta00759d}{6606}}{}{}
\setlength{\parskip}{-8pt}
}



\begin{multicols}{2}
    \section{\hei Awards}
    
    % Restore normal labels
    %\tltext{\scriptsize}
    
    {
        \setlength{\parskip}{-5pt}
        \tldatelabelcventry{2017/10}{2017.10}{Xianfeng Scholarship for Phys. Chem.}{PKU}{}{}{}
        
        \setlength{\parskip}{-20pt}
        
        \tldatelabelcventry{2016/10}{2016.10}{President's Ph.D. Scholarship}{PKU}{}{}{}
        
        \setlength{\parskip}{-10pt}
        
        \tlcventry{2015/9}{2019/10}{Merit Student $\times3$}{PKU}{}{}{}
        
        \setlength{\parskip}{2pt}
        
        \tlcventry{2011/9}{2015/7}{Wusi Scholarship, Xianfeng Scholarship}{PKU}{}{}{}   
    }
    
    \section{\hei Miscellanies}
    {
        \begin{itemize}
%            \setlength{\parskip}{2pt}
            \item {$\mathbf{Teaching\,Assistant}$}: Comprehensive Physical Chemistry (2017 and 2018 Spring semesters).
            \item {$\mathbf{Translation}$}: Japanese interview and subtitle. General scientific article for publication in \textit{Scientific American} (Chinese).
            \item {$\mathbf{Blog}$}: technical writings on scientific programming and computation at homepage.
            \item {$\mathbf{Sports}$}: running, basketball, softball
        \end{itemize}
    }

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../"
%%% End:
